---
title: "Profitability vs Sales Dashboard"
author: "Dao Dang"
format: dashboard
theme: solar
---

```{r}
library(lessR)
style(suggest=FALSE, quiet=TRUE)  # turn off suggestions and text output
style(lab_cex=1.6, axis_cex=1.3)  # enlarge axis labels and value labels
```

```{r}
library(openxlsx)
```

```{r echo=FALSE}

d <- Read("https://web.pdx.edu/~gerbing/data/Superstore.xlsx")

```

## Row {height="20%"}

::: {.valuebox icon="caret-right-fill" color="info" style="color: gray"}
**Total Sales**

`r d$Sale |> sum() |> round(digits=0) |> prettyNum(big.mark=",")`
:::

::: {.valuebox icon="caret-right-fill" color="secondary" style="color: pink"}
**Total Profit**

`r d$Profit |> sum() |> round(digits=0) |> prettyNum(big.mark=",")`
:::

::: {.valuebox icon="caret-right-fill" color="success" style="color: blue"}
**Number of Customers**

`r length(unique(d$Customer.Name))`
:::

## Row {height="20%"}

::: {.card title="Total Sales"}
Chairs and Phones are products have the highest total sales with 14% while Fasteners are products had the lowest sold.
:::

::: {.card title="Total Profits"}
Copiers has the highest profit even it got 6% of total sales. However, one thing we need to concern and investigate more is Tables and Bookcases are products that we got negative profit.
:::

::: {.card title="Interpret"}
Chairs and Phones are products have the highest total sales with 14% while Fasteners has the lowest sold. Copiers has the highest profit even it got 6% of total sales. However, one thing we need to concern and investigate more is Tables and Bookcases are products that we got negative profit.
:::

## Row {height="59%"}

```{r}
BarChart(SubCategory, Sales, stat="sum", rotate_x = 90)
```

```{r}
BarChart(SubCategory, Profit, stat="sum", rotate_x = 90)
```

```{r}
Plot(Sales, Profit)
```
